\bf Fast Neural Machine Translation Implementation

### 2018-05-17 wnmt.2018/wnmt.tex
turn on timings

% \mtsummitHeader{x}{x}{xxx-xxx}{2016}{45-character paper description goes here}{Author(s) initials and last name go here}
\title{\bf Focusing on Fast Neural Network Inference}

\author{\name{\bf Hieu Hoang} \hfill  \addr{hieu@hoang.co.uk}\\ 
        \addr{}
\AND
       \name{\bf Tomasz Dwojak} \hfill \addr{???}\\
        \addr{Adam Mickiewicz University}
\AND
       \name{\bf Kenneth Heafield} \hfill \addr{???}\\
       %\name{\bf Kenneth Heafield} \hfill \addr{kheafiel@inf.ed.ac.uk}\\
        \addr{University of Edinburgh, Scotland}
}

>>>>

% \mtsummitHeader{x}{x}{xxx-xxx}{2016}{45-character paper description goes here}{Author(s) initials and last name go here}
\title{\bf Fast Neural Machine Translation Implementation}

\author{\name{\bf Hieu Hoang} \hfill  \addr{hieu@hoang.co.uk}\\ 
        \addr{}
\AND
       \name{\bf Tomasz Dwojak} \hfill \addr{t.dwojak@amu.edu.pl}\\
        \addr{Adam Mickiewicz University}
\AND
       \name{\bf Rihards Krislauks} \hfill \addr{rihards.krislauks@tilde.lv}\\
        \addr{Tilde}
\AND
       \name{\bf Daniel Torregrosa} \hfill \addr{dtorregrosa@dlsi.ua.es}\\
        \addr{Universitat d’Alacant}
\AND
       \name{\bf Kenneth Heafield} \hfill \addr{kheafiel@inf.ed.ac.uk}\\
       %\name{\bf Kenneth Heafield} \hfill \addr{kheafiel@inf.ed.ac.uk}\\
        \addr{University of Edinburgh, Scotland}
}
